Automatically generated NE tagged corpora for English and Hungarian

### 2012-04-27 paper/engNERwiki.tex
Added the download URL; changed a few things here and there.

Our goal is to create a large NE annotated corpus, automatically generated from Wikipedia articles. We follow a similar path to Nothman et al.~\shortcite{Nothman:08} and we broke down the process into four steps:

\begin{enumerate}
\item Classify Wikipedia articles into entity classes.
\item Parse Wikipedia and split articles into sentences.
\item Label named entities in the text.
\item Select which sentences are included in the corpus.
\end{enumerate}

@@

The following sub-sections describe how the method explained above can be improved to increase precision, sentence coverage and to account for peculiarities in the CoNLL guidelines.

@@

The corpora are available under the Creative Commons Attribution-Sharealike 3.0 Unported License (CC-BY-SA), the same license under which the text of Wikipedia is released. The data files can be freely downloaded from XXX. The corpora will also be distributed through META-SHARE network, which is an open, distributed facility for exchanging and sharing resources, and is one of the lines of action of META-NET, a Network of Excellence funded by the European Commission.

>>>>

Our goal is to create a large NE annotated corpus, automatically generated from Wikipedia articles. Following Nothman et al.~\shortcite{Nothman:08}, we broke down the process into four steps:

\begin{enumerate}
\item Classify Wikipedia articles into entity classes
%\item Parse Wikipedia and split articles into sentences
\item Parse Wikipedia into sentences
\item Label named entities in the text
\item Select the sentences to include in the corpus
\end{enumerate}

@@

The following sub-sections describe how the method explained above can be improved to increase precision, sentence coverage and to account for peculiarities in English orthography and the CoNLL guidelines.

@@

The corpora are available under the Creative Commons Attribution-Sharealike 3.0 Unported License (CC-BY-SA), the same license under which the text of Wikipedia is released. The data files can be freely downloaded from \texttt{http://hlt.sztaki.hu}. The corpora will also be distributed through META-SHARE network, which is an open, distributed facility for exchanging and sharing resources, and is one of the lines of action of META-NET, a Network of Excellence funded by the European Commission.
